%% LaTeX source of Bibliography of the thesis.
%% NEVER compile this file. Complie 'thesis.tex' instead.

\begin{thebibliography}{99}

\bibitem{Rosen.2012}
	K. H. Rosen.
	\emph{Discrete Mathematics and Its Applications 7th edition} [M].
	McGraw-Hill Education, 2012. 641-744.

\bibitem{Harper.2004}
	L. H. Harper.
	\emph{Global Methods for Combinatorial Isoperimetric Problems} [M].
	Cambridge University Press, 2004. 1-19.

\bibitem{Guu.1997}
	C. Guu.
	\emph{The Circular Wirelength Problem for Hypercubes} [D].
	California: University of California, Riverside, 1997.

\bibitem{Manuel.2009}
	P. Manuel, I. Rajasingh, B. Rajan, H. Mercy.
	\emph{Exact wirelength of hypercubes on a grid} [J].
	Discrete Applied Mathematics, 2009, 157(7): 1486-1495.

\bibitem{Manuel.2011}
	P. Manuel, M. Arockiaraj, I. Rajasingh, B. Rajan.
	\emph{Embedding hypercubes into cylinders, snakes and caterpillars for
	minimizing wirelength} [J].
	Discrete Applied Mathematics, 2011, 159(17): 2109-2116.

\bibitem{Opatrny.2000}
	J. Opatrny, D. Sotteau.
	\emph{Embeddings of complete binary trees into grids and extended grids
	with total vertex-congestion 1} [J].
	Discrete Applied Mathematics, 2000, 98(3): 237-254.

\bibitem{Harper.1964}
	L. H. Harper.
	\emph{Optimal assignments of numbers to vertices} [J].
	Journal of the Society for Industrial and Applied Mathematics,
	1964, 12(1): 131-135.

\bibitem{Erbele.2003}
	J. Erbele, J. Chavez, R. Trapp.
	\emph{The Cyclic Cutwidth of $Q_n$} [J/OL].
	California State University, San Bernardino, 2003.

\bibitem{Bezrukov.2000}
	S. L. Bezrukov, J. D. Chavez, L. H. Harper, M. Röttger, U.-P. Schroeder.
	\emph{The Congestion of $n$-Cube Layout on a Rectangular Grid} [J].
	Discrete Mathematics, 2000, 213(1-3): 13-19.

\bibitem{Ji.2015}
	W. Ji, Q. Liu, G. Wang, Z. Shen.
	\emph{Embedding of Hypercube into Cylinder} [J/OL].
	arXiv: 1511.07932, 2015.

\bibitem{Bernstein.1967}
	A. J. Bernstein.
	\emph{Maximally connected arrays on the n-cube} [J].
	SIAM Journal on Applied Mathematics, 1967, 15(6): 1485-1489.

\bibitem{Dean.2004}
	J. Dean, S. Ghemawat.
	\emph{MapReduce: Simplified Data Processing on Large Clusters} [J].
	Communications of the ACM, 2008, 51(1): 107-113.

\bibitem{Harper.1966}
	L. H. Harper.
	\emph{Optimal Numberings and Isoperimetric Problems on Graphs} [J].
	Journal of Combinatorial Theory, 1966, 1(3): 385-393.

\bibitem{Steiglitz.1965}
	K. Steiglitz, A. J. Bernstein.
	\emph{Optimal Binary Coding of Ordered Numbers} [J].
	Journal of the Society for Industrial and Applied Mathematics,
	1965, 13(2): 441-443.

\bibitem{Chavez.1998}
	J. D. Chavez, R. Trapp.
	\emph{The cyclic cutwidth of trees} [J].
	Discrete Applied Mathematics, 1998, 87(1-3), 25-32.

\bibitem{citekey}
	M. Zaharia, M. Chowdhury, M. J. Franklin, S. Shenker, I. Stoica.
	\emph{Spark: Cluster Computing with Working Sets} [A].
	In: Proceedings of the 2nd USENIX Conference on Hot Topics in Cloud Computing [C].
	Boston, MA: USENIX Association, 2010. 10-10.

\bibitem{Zaharia.2012}
	M. Zaharia, M. Chowdhury, T. Das, A. Dave, J. Ma,
	M. McCauley, M. J. Franklin, S. Shenker, I. Stoica.
	\emph{Resilient Distributed Datasets: A Fault-tolerant Abstraction for
	In-memory Cluster Computing} [A].
	In: Proceedings of the 9th USENIX Conference on Networked Systems Design and Implementation [C].
	San Jose, CA: USENIX Association, 2012. 15-28.

\end{thebibliography}
